Characterization of gaps in directly bonded Si compound optics

### 2014-02-17 AO_bondedSi.tex
minor tweaks, just pushing to remote

\begin{table}[h!]
  \caption{A simple table}
  \begin{center}
    \begin{tabular}{ |p{8cm}| p{8cm} | p{2.2cm} |}
    \hline
    Appearance of spectra & Interpretation & Exemplars \\
    \hline
    Measurement within the prediction band & Life is good & VS21-M1, Figure \ref{VS21specm1}, VG15, VG07\\
    \hline
    Measured spectrum below the prediction band but shape is similar & Gap was slightly larger than predicted or bonding was incomplete& VS21-F1, Figure \ref{VS21specf1}, VS09, VG15, \\
    \hline
    Measured spectrum above the prediction band but shape is similar & Gap was slightly smaller than predicted & VS21-M2\\
    \hline
    Measured spectrum exceeds DSP reference puck & unanticipated anti-reflection coating on the surface of the Si sample (e.g. Sharpie marker residue) & VG08\\
    \hline
    High frequency, low amplitude wiggles superimposed upon smooth underlying trend & Large, unanticipated gap, with a small fill factor  & VS21-C3\\   
     																			     & wavelength dependent diffraction from the mesh patterns & VS21-C3\\       
     																			     & measurement artifact  & VS21-C3\\       												
    \hline
    Non-unit transmission constant with wavelength (gray spectrum) & Artifact of measurement- vignetting of beam, absorptive coating, zero-point drift & VS21-C4 \\
    \hline
    Completely different spectrum than anticipated with low absolute transmission & Large, inhomogeneous gap which should appear as an IR bubble & VG09 \\
    \hline
    \end{tabular}
  \end{center}
\end{table}

>>>>

\begin{table}[h!]
  \caption{Interpretation of the diversity of IR spectra}
  \begin{center}
    \begin{tabular}{ |p{8cm}| p{8cm} | p{2.2cm} |}
    \hline
    Appearance of spectra & Interpretation & Exemplars \\
    \hline
    Measurement within the prediction band & Life is good & VS21-M1, Figure \ref{VS21specm1}, VG15, VG07\\
    \hline
    Measured spectrum below the prediction band but shape is similar & Gap was slightly larger than predicted or bonding was incomplete& VS21-F1, Figure \ref{VS21specf1}, VS09, VG15, \\
    \hline
    Measured spectrum above the prediction band but shape is similar & Gap was slightly smaller than predicted & VS21-M2\\
    \hline
    Measured spectrum exceeds DSP reference puck & unanticipated anti-reflection coating on the surface of the Si sample (e.g. Sharpie marker residue) & VG08\\
    \hline
    High frequency, low amplitude wiggles superimposed upon smooth underlying trend & Large, unanticipated gap, with a small fill factor  & VS21-C3\\   
     																			     & wavelength dependent diffraction from the mesh patterns & VS21-C3\\       
     																			     & measurement artifact  & VS21-C3\\       												
    \hline
    Non-unit transmission constant with wavelength (gray spectrum) & Artifact of measurement- vignetting of beam, absorptive coating, zero-point drift & VS21-C4 \\
    \hline
    Completely different spectrum than anticipated with low absolute transmission & Large, inhomogeneous gap consistent with an IR bubble & VG09 \\
    \hline
    \end{tabular}
  \end{center}
\end{table}
